### 2017-10-16 src/2_Finance.tex
new bid ask spread plot

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket1.png}
  \caption[HFT market share in the US and Europe]{HFT market share in the US. Source: TABB Group.}
  \label{fig:HFTmarket1}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket2.png}
  \caption[Revenue in the US]{Revenue in the US. Source: TABB Group.}
  \label{fig:HFTmarket2}
\end{figure}
US market revenues have fallen dramatically. Figure~\ref{fig:HFTmarket2} shows how revenues in US stocks have fallen the last years. One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.

On the other hand, HFT has been criticised on qualitative issues concerning
fairness and systemic risk. However, empirical research shows that HFT has lead to
beneficial impacts such as reducing spreads (difference between buyers and
sellers prices), increased liquidity, allowing more efficient price formation,
reduced transaction costs and lower market volatility. HFT makes the stock market more efficient and helps small investors who trade at random times over the day.

>>>>

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.9\textwidth]{img/HFTmarket1.png}
  \caption[HFT market share in the US and Europe]{HFT market share in the US. Source: TABB Group.}
  \label{fig:HFTmarket1}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.9\textwidth]{img/HFTmarket2.png}
  \caption[Revenue in the US]{Revenue in the US. Source: TABB Group.}
  \label{fig:HFTmarket2}
\end{figure}
US market revenues have fallen dramatically. Figure~\ref{fig:HFTmarket2} shows how revenues in US stocks have fallen the last years. One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.

On the other hand, HFT has been criticised on qualitative issues concerning
fairness and systemic risk. However, HFT has lead to
beneficial impacts such as reducing spreads (difference between buyers (bid) and
sellers (ask) prices), increased liquidity, allowing more efficient price formation,
reduced transaction costs and lower market volatility.

\begin{figure}[!ht]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.7\textwidth]{img/bid-ask-spreads.jpg}
  \caption[Bid-ask spreads]{Bid-ask spreads for large and small caps stock US. Source: Credit Suisse.}
  \label{fig:Spreads}
\end{figure}
In figure \ref{fig:Spreads}  shows the Bid-ask spread for large and small caps. A large cap refers to an asset with market capitalisation value of more than \$10 billion dollars.

In theory, Bid-ask spreads for large caps and small caps move on the same direction, meaning they both are affected by volatility. This scenario is only true until 2009, where the large caps (in red) gets tight spreads and small caps have wider  spreads, suggesting a concentrating of trading in the most liquid, biggest stocks.
